Mergeable Types

### 2017-02-26 paper/model.tex

The merge operation for lists is composed of two separate functions,
\C{edit\_seq} and \C{op\_transform}.
\begin{itemize}
  \item \C{edit\_seq} takes a pair of lists, \C{v} and $\C{v'}$, and
  computes the shortest sequence of list operations that need to be
  applied on \C{v} to obtain \C{v'}. Such a sequence is called an
  \emph{edit sequence}. The length of the sequence corresponds to the
  standard notion of the \emph{edit distance} between the two lists,
  which can be computed in polynomial time, for e.g., using the
  Wagner-Fisher algorithm~\cite{wagner-fischer}. A slight modification
  of Wagner-Fischer also lets us compute the edit sequence. The
  implementation in Fig.~\ref{fig:mlist} represents edits using the
  type \C{edit}. Constructors \C{I}, \C{D}, and \C{S} stand for
  \C{insert}, \C{delete}, and \C{subst}, respectively; \C{Nop} is
  there for technical reasons. The subst constructor also carries the
  \C{A.t} element that was substituted. Our implementation of
  Wagner-Fischer is more-or-less standard (hence, not shown), except
  that the edit sequence it returns orders \C{I}'s and \C{D}'s before
  \C{S}'s.  Fig.~\ref{fig:list-eg} illustrates edit sequences for a
  sample list. The sequence \C{[I(c,0); S(3,c,s)]} maps the list
  \C{[a;b;c]} to \C{[c;a;b;s]} because \C{subst 3 s (insert c 0
  [a;b;c]) = [c;a;b;s]}.
  \item  \C{op\_transform} takes a pair of edit sequences, $s_1$ and
  $s_2$, that map a list $v$ to two different lists, $v_1$ and $v_2$
  (e.g., Fig.~\ref{fig:list-eg}), and transforms $s_1$ to $s_1'$ such
  that $s_1'$ has the same effect on $v_2$ as $s_1$ had on $v$.  For
  instance, in Fig.~\ref{list-eg}, let $s_1$ be the edit sequence
  \C{[D(1); S(d,1)]}, which maps the list \C{[a;b;c]} ($v$) to
  \C{[a;d]} ($v_1$). The \C{D} edit deletes the first element of $v$.
  However, if $s_1$ is to be applied on the list \C{[c;a;b;s]}
  ($v_2$), which has a new element at position 0, the \C{D} edit must
  delete the the second element from $v_2$, if it were to have the
  same effect as it did on $v$. We say \C{D(1)} in $s_1$ has to be
  transformed w.r.t the sequence $s_2 = \C{[I(c,0);S(3,c,s)]}$.  The
  function \C{op\_transform} of Fig.~\ref{fig:mlist-xform} computes
  such \emph{operational transformation} for the sequence \C{mine}
  w.r.t the sequence \C{others}, and returns \C{mine'} as the
  transformed sequence.  
\end{itemize}

>>>>

The merge operation for lists is composed of two separate functions,
\C{edit\_seq} and \C{op\_transform}.
\begin{itemize}
  \item \C{edit\_seq} takes a pair of lists, \C{v} and $\C{v'}$, and
  computes the shortest sequence of list operations that need to be
  applied on \C{v} to obtain \C{v'}. Such a sequence is called an
  \emph{edit sequence}. The length of the sequence corresponds to the
  standard notion of the \emph{edit distance} between the two lists,
  which can be computed in polynomial time, for e.g., using the
  Wagner-Fisher algorithm~\cite{wagner-fischer}. A slight modification
  of Wagner-Fischer also lets us compute the edit sequence. The
  implementation in Fig.~\ref{fig:mlist} represents edits using the
  type \C{edit}. Constructors \C{I}, \C{D}, and \C{S} stand for
  \C{insert}, \C{delete}, and \C{subst}, respectively; \C{Nop} is
  there for technical reasons. The subst constructor also carries the
  \C{A.t} element that was substituted. Our implementation of
  Wagner-Fischer is more-or-less standard (hence, not shown), except
  that the edit sequence it returns orders \C{I}'s and \C{D}'s before
  \C{S}'s.  Fig.~\ref{fig:list-eg} illustrates edit sequences for a
  sample list. The sequence \C{[I(c,0); S(3,c,s)]} maps the list
  \C{[a;b;c]} to \C{[c;a;b;s]} because \C{subst 3 s (insert c 0
  [a;b;c]) = [c;a;b;s]}.
  \item  \C{op\_transform} takes a pair of edit sequences, $s_1$ and
  $s_2$, that map a list $v$ to two different lists, $v_1$ and $v_2$
  (e.g., Fig.~\ref{fig:list-eg}), and transforms $s_1$ to $s_1'$ such
  that $s_1'$ has the same effect on $v_2$ as $s_1$ had on $v$.  For
  instance, in Fig.~\ref{list-eg}, let $s_1$ be the edit sequence
  \C{[D(1); S(d,1)]}, which maps the list \C{[a;b;c]} ($v$) to
  \C{[a;d]} ($v_1$). The \C{D} edit deletes the first element of $v$.
  However, if $s_1$ is to be applied on the list \C{[c;a;b;s]}
  ($v_2$), which has a new element at position 0, the \C{D} edit must
  delete the the second element from $v_2$, if it were to have the
  same effect as it did on $v$. We say \C{D(1)} in $s_1$ has to be
  transformed w.r.t the sequence $s_2 = \C{[I(c,0);S(3,c,s)]}$.  The
  function \C{op\_transform} of Fig.~\ref{fig:mlist-xform} computes
  such \emph{operational transformation} for the sequence \C{mine}
  w.r.t the sequence \C{others}, and returns \C{mine'}, the
  transformed sequence. To do so, it first pulls the \C{S} edits in
  \C{mine} to the beginning of the sequence, transforming them w.r.t
  the \C{I} and \C{D} edits in \C{mine}. Having all the \C{S} edits at
  the beginning of the \C{mine} sequence makes their transformation
  easier since the offset of the transformed substitution depends only
  on the edits in the \C{other} sequence. Furthermore, it facilitates
  an easy comparison with \C{S} edits at the end of \C{other}. Next,
  \C{op\_transform} transforms edits in \C{mine} w.r.t \C{other} by
  comparing their offsets; the rules are straightforward.
\end{itemize}
